The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

The main purpose of this study is to use 3D\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{oblique} jet scenario is able to produce\
the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.

>>>>

The main purpose of this study is to use 3D\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{oblique} jet scenario is able to produce\
the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
and of microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
